---
title: "Appendix"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.width = 6, fig.height = 5)
```

```{r}
library(stringr)
library(car)
library(faraway)
library(ggplot2)
library(corrgram)
library(stringr)
library(leaps)
library(corrgram)
library(gridExtra)
library(corrplot)
```

We read the data into a data frame called ```airbnb```.
```{r}
airbnb = read.csv("listings.csv")
```

## Data Wrangling

We count how many NA's each variable has. We exclude the variables where the majority of values are NA's. Four variables are excluded.

```{r}
countNA = 0
for (i in 1:ncol(airbnb)){
  
  countNA[i] = sum(is.na(airbnb[, i]))
  
}

airbnb = airbnb[, -which(countNA > 14000)]
```

Next, we exclude variables that do not provide relevant information in order to predict the price of listings. That being said, we keep the following variables. Variable ```neighbourhood_cleansed``` is renamed to ```neighbourhood```.

```{r}
variables = c('neighbourhood_cleansed',
              'property_type',
              'room_type',
              'accommodates',
              'bathrooms',
              'bedrooms',
              'beds',
              'price',
              'cleaning_fee',
              'availability_30',
              'number_of_reviews',
              'review_scores_rating',
              'reviews_per_month')

airbnb = airbnb[, variables]
colnames(airbnb)[1] = 'neighbourhood'
```

Observations that contain NAs in at least on of the columns, are excluded. 

```{r}
airbnb = na.omit(airbnb)
```

Variables ```price``` and ```cleaning_fee``` need to be converted to numeric, since they are of class ```factor```. 

```{r}
airbnb$price = as.character(airbnb$price)
airbnb$price = str_replace(airbnb$price, ",", "")
airbnb$price = as.numeric(str_sub(airbnb$price, 2))

airbnb$cleaning_fee = as.character(airbnb$cleaning_fee)
airbnb$cleaning_fee = str_replace(airbnb$cleaning_fee, ",", "")
airbnb$cleaning_fee = as.numeric(str_sub(airbnb$cleaning_fee, 2))

indices = which(is.na(airbnb$cleaning_fee))
airbnb[indices, "cleaning_fee"] = 0
```

We remove levels of ```property_type``` with less than or equal to five observations. There are 10 such levels.
```{r}

table(airbnb$property_type)
airbnb = airbnb[!as.numeric(airbnb$property_type) %in% 
                                  which(table(airbnb$property_type) <= 5), ]    

airbnb$property_type = droplevels(airbnb$property_type)

```

## Exploratory Data Analysis

Side-by-side boxplots of logarithm of price, for each neighbourhood.

```{r, fig.width = 7, fig.height = 7}
ggplot(airbnb, 
       aes(x = as.numeric(airbnb$neighbourhood), 
           y = log(airbnb$price), 
           fill = airbnb$neighbourhood)) + 
    geom_boxplot(alpha = .6, outlier.alpha = .4) +
    scale_y_continuous(name = "Logarithm of Price") + 
    scale_x_discrete(name = "Neighbourhoods") + 
    theme_minimal() +
    theme(axis.title.x = element_text(size = 12),
          axis.title.y = element_text(size = 12),
          axis.text.y = element_text(size = 10),
          legend.position = "bottom") + 
    theme(legend.text = element_text(size = 8)) + 
    labs(fill = "")
```

Correlograms represent pairwise correlations between each variable.

```{r, fig.width = 8, fig.height = 8}
col = colorRampPalette(c("#BB4444", "#EE9988", "#FFFFFF", "#77AADD", "#4477AA"))
corrplot(cor(as.matrix(airbnb[, 4:ncol(airbnb)])), method = "color", col = col(200),  
         type = "upper", order = "hclust", 
         addCoef.col = "black", 
         tl.col = "black", tl.srt = 45, 
         diag = FALSE)

```

Boxplots of logarithm of price, for each property type.

```{r}
ggplot(airbnb, 
       aes(x = as.numeric(airbnb$property_type), 
           y = log(airbnb$price), 
           fill = airbnb$property_type)) + 
    geom_boxplot(alpha = .6, outlier.alpha = 0.4) + 
    scale_y_continuous(name = "Logarithm of Price") + 
    scale_x_discrete(name = "Property Type") + 
    theme_minimal() +
    theme(axis.text.y = element_text(size = 10),
          axis.title.x = element_text(size = 11),
          axis.title.y = element_text(size = 11),
          legend.position = "bottom",
          legend.text = element_text(size = 8)) + 
    scale_fill_brewer(palette = "Paired") + 
    labs(fill = "")
```

Boxplots of logarithm of price, for each room type.

```{r}
ggplot(airbnb, 
       aes(x = as.numeric(airbnb$room_type), 
           y = log(airbnb$price), 
           fill = airbnb$room_type)) + 
    geom_boxplot(alpha = 0.6, outlier.alpha = 0.4) + 
    scale_y_continuous(name = "Logarithm of Price") + 
    scale_x_discrete(name = "Room Type") +
    theme_minimal() +
    theme(axis.text.y = element_text(size = 10), 
          axis.title.x = element_text(size = 11),
          axis.title.y = element_text(size = 11),
          legend.text = element_text(size = 9),
          legend.position = "bottom") +
  scale_fill_brewer(palette = "Set1") +
  labs(fill = "")
```

Histogram of price.

```{r}
ggplot(data = airbnb, 
       aes(airbnb$price)) + 
    geom_histogram(bins = 50, 
                   col = "#000000", 
                   fill = "#99FFFF", 
                   alpha = .5) + 
    labs(x = "Price", y = "Frequency") + 
    scale_x_continuous(breaks = c(seq(0, 800, 200),1000, 1500, 2000)) +
    scale_y_continuous(breaks = c(seq(0, 4000, 1000), 4600)) +
    theme_minimal() + 
    theme(axis.text.x = element_text(size = 10), 
          axis.text.y = element_text(size = 10),
          axis.title.x = element_text(size = 11),
          axis.title.y = element_text(size = 11))

```

Scatterplots of logarithm of price with respect to accommodates, bathrooms, bedrooms, and beds, respectively.

```{r}
p1 = ggplot(airbnb, 
             aes(x = airbnb$accommodates, 
                 y = log(airbnb$price))) + 
    geom_point(alpha = 0.4) + 
    labs(y = 'Logarithm of Price', x = 'Accommodates') +
    theme_minimal() +
    scale_x_continuous(breaks = seq(1, 17, 2)) +
    theme(axis.text.x = element_text(size = 10),
          axis.text.y = element_text(size = 10),
          axis.title.x = element_text(size = 12),
          axis.title.y = element_text(size = 12))

p2 = ggplot(airbnb, 
            aes(x = airbnb$bathrooms, 
                y = log(airbnb$price))) + 
    geom_point(alpha = 0.4) + 
    theme_minimal() +
    labs(x = 'Bathrooms', y = '') +
    theme(axis.text.x = element_text(size = 10),
          axis.text.y = element_text(size = 10),
          axis.title.x = element_text(size = 12),
          axis.title.y = element_text(size = 12))

p3 = ggplot(airbnb, 
            aes(x = airbnb$bedrooms, 
                y = log(airbnb$price))) + 
    geom_point(alpha = 0.4) + 
    theme_minimal() +
    labs(x = 'Bedrooms', y = 'Logarithm of Price') +
    scale_x_continuous(breaks = seq(0, 10, 2)) +
    theme(axis.text.x = element_text(size = 10),
          axis.text.y = element_text(size = 10),
          axis.title.x = element_text(size = 12),
          axis.title.y = element_text(size = 12))

p4 = ggplot(airbnb, 
            aes(x = airbnb$beds, 
                y = log(airbnb$price))) + 
    geom_point(alpha = 0.4) + 
    theme_minimal() +
    labs(x = 'Beds', y = '') +
    scale_x_continuous(breaks = seq(0, 16, 2)) +
    theme(axis.text.x = element_text(size = 10),
          axis.text.y = element_text(size = 10),
          axis.title.x = element_text(size = 12),
          axis.title.y = element_text(size = 12))

grid.arrange(p1,p2,p3,p4)
```

Scatterplot of logarithm of price and cleaning fee.

```{r}
p5 = ggplot(airbnb, 
            aes(x = airbnb$cleaning_fee, 
                y = log(airbnb$price))) + 
    geom_point(alpha = 0.4) + 
    theme_minimal() +
    labs(x = 'Cleaning Fee', y = 'Logarithm of Price') +
    theme(axis.text.x = element_text(size = 12),
          axis.text.y = element_text(size = 12),
          axis.title.x = element_text(size = 14),
          axis.title.y = element_text(size = 14))
p5
```

## Variable Selection

Check for significance of each variable. We use the ```drop1()``` function. Variable ```number_of_reviews``` is not statistically significant. The variable is removed from the model. The p-value is 0.5185.
```{r}
initialModel = lm(price ~ neighbourhood + 
                       property_type + 
                       room_type + 
                       accommodates + 
                       bathrooms + 
                       bedrooms + 
                       beds + 
                       cleaning_fee + 
                       availability_30 + 
                       number_of_reviews + 
                       review_scores_rating + 
                       reviews_per_month, data = airbnb)
```

```{r}
drop1(initialModel, test = "F")
initialModel2 = lm(price ~ accommodates + 
                     bathrooms + 
                     bedrooms + 
                     beds + 
                     cleaning_fee + 
                     availability_30 + 
                     review_scores_rating + 
                     reviews_per_month, data = airbnb)

```

Function ```vif()``` examines for multicolinearity between regressors.

```{r}
vif(initialModel2)
```

The ```leaps()``` function employs an exhaustive search and reports the adjusted $R^2$. It works only for quantitative variables, so these are extracted in a data frame called ```airbnbQualitative```.
```{r}
price = airbnb$price
airbnbQualitative = airbnb[ ,-c(1,2,3,8,11)]
fullModelQualitative = lm(price ~ ., data = airbnbQualitative)
summary(fullModelQualitative)

modelMatrixQual = model.matrix(fullModelQualitative)[ ,-1]

adjustedR2 = leaps(modelMatrixQual, price, method = 'adjr2', nbest = 30)
maxadjr(adjustedR2, 25)
```

The selected model from ```leaps()``` contains four quantitative variables, specifically, ```accommodates, bedrooms, cleaning_fee``` and ```availability_30```. It explains 0.41\% of variance in the data. The selected model is combined with the three remaining factor variables.

```{r}
airbnb = cbind(airbnb$neighbourhood, 
               airbnb$property_type, 
               airbnb$room_type, 
               airbnbQualitative[, c(1,3,5,6)])

colnames(airbnb) = c('neighbourhood', 
                     'property_type', 
                     'room_type', 
                     'accommodates', 
                     'bedrooms', 
                     'cleaning_fee', 
                     'availability_30')

airbnb$price = price
```

Next, the significance of each factor variable with respect to the increase of the adjusted $R^2$ is examined. It is known that all three factor variables are significant as shown from the output of ```drop1()``` function. We remove the variable that does not increase the adjusted $R^2$ significantly.       

First, variable ```room_type``` is removed.
```{r}
fullModel = lm(price ~ ., data = airbnb)
summary(fullModel)$adj.r.squared

cat('Remove room_type')
reducedModel1 = lm(price ~ accommodates + 
                    bedrooms + 
                    cleaning_fee + 
                    availability_30 + 
                    neighbourhood + 
                    property_type, data = airbnb)
summary(reducedModel1)$adj.r.squared
```

The removal of ```property_type``` follows.
```{r}
reducedModel2 = lm(price ~ accommodates + 
                    bedrooms + 
                    cleaning_fee + 
                    availability_30 + 
                    neighbourhood + 
                    room_type, data = airbnb)
summary(reducedModel2)$adj.r.squared
```

Finally, we remove ```neighbourhood```.
```{r}
reducedModel3 = lm(price ~ accommodates + 
                    bedrooms + 
                    cleaning_fee + 
                    availability_30 + 
                    property_type + 
                    room_type, data = airbnb)
summary(reducedModel3)$adj.r.squared
```

Variable ```property_type``` is removed from the model, since it provides the least increase in adjusted $R^2$. 
```{r}
airbnb = airbnb[, -2]
fullModel = reducedModel2
```

We examine which interactions between quantitative and qualitative variables are statistically significant. We decided to keep two interactions; those that result in the largest decrease in Residual Sum of Squares (RSS).

```{r}
anova(update(fullModel, . ~ . + neighbourhood:cleaning_fee))[7, ]
anova(update(fullModel, . ~ . + neighbourhood:availability_30))[7, ]
anova(update(fullModel, . ~ . + room_type:accommodates))[7, ]
anova(update(fullModel, . ~ . + room_type:cleaning_fee))[7, ]
anova(update(fullModel, . ~ . + room_type:availability_30))[7, ]
```

The model containing the interaction ```neighbourhood:cleaning_fee``` provided the largest decrease in RSS (565551). We add the interaction to the model.

```{r}
fullModel = update(fullModel, . ~ . + neighbourhood:cleaning_fee)
```

The model that includes interaction ```neighbourhood:availability_30``` results in the largest decrease in RSS (given that we have added ```neighbourhood:cleaning_fee```). The model is updated by adding this interaction as well.

```{r}
anova(update(fullModel, . ~ . + neighbourhood:availability_30))[8, ]
anova(update(fullModel, . ~ . + room_type:accommodates))[8, ]
anova(update(fullModel, . ~ . + room_type:cleaning_fee))[8, ]
anova(update(fullModel, . ~ . + room_type:availability_30))[8, ]

fullModel = update(fullModel, . ~ . + neighbourhood:availability_30)
```

The model explains 51.7\% of variance in the data. The Q-Q plot indicates large deviations from normality.
```{r}
summary(fullModel)$adj.r.squared
qqPlot(fullModel$residuals, 
       ylab = "", 
       xlab = "")
mtext("Residuals", side = 2, line = 2.6, cex = 1)
mtext("Normal Quantiles", side = 1, line = 2.6, cex = 1)
```

We use the $\log$ transformation for the response. The following plot represents the Q-Q plot of the residuals after the transformation. Although the residuals seem to be more normally distributed, deviation from normality is still apparent. The adj. $R^2$ is equal to 0.59. For the rest of the analysis, the $\log$ transformation is used for the response.

```{r}
fullModelLog = lm(log(price) ~ accommodates + 
                      bedrooms + 
                      cleaning_fee + 
                      availability_30 + 
                      neighbourhood + 
                      room_type + 
                      neighbourhood:cleaning_fee + 
                      neighbourhood:availability_30 , data = airbnb)
summary(fullModelLog)$adj.r.squared
qqPlot(fullModelLog$residuals, 
       ylab = "", 
       xlab = "")
mtext("Residuals", side = 2, line = 2.6, cex = 1)
mtext("Normal Quantiles", side = 1, line = 2.6, cex = 1)
```

## Model Selection

Next, 21 models that contain different combinations of variables with interactions, polynomial terms of second order, and logarithm transformations are defined.

```{r}
models = c(log(price) ~ accommodates + # 1
               bedrooms + 
               cleaning_fee + 
               availability_30 + 
               neighbourhood + 
               room_type,
           log(price) ~ poly(accommodates, 2) + # 2
               bedrooms + 
               cleaning_fee + 
               availability_30 + 
               neighbourhood + 
               room_type,
           log(price) ~ accommodates + # 3
               poly(bedrooms, 2) + 
               cleaning_fee + 
               availability_30 + 
               neighbourhood + 
               room_type,
           log(price) ~ poly(accommodates, 2) + # 4
               poly(bedrooms, 2) + 
               cleaning_fee + 
               availability_30 + 
               neighbourhood + 
               room_type,
           log(price) ~ log(accommodates) + # 5
               bedrooms + 
               cleaning_fee + 
               availability_30 + 
               neighbourhood + 
               room_type,
           log(price) ~ accommodates + # 6
               log(bedrooms + 1) + 
               cleaning_fee + 
               availability_30 + 
               neighbourhood + 
               room_type,
           log(price) ~ log(accommodates) + # 7
               log(bedrooms + 1) + 
               cleaning_fee + 
               availability_30 + 
               neighbourhood + 
               room_type,
           log(price) ~ accommodates + # 8
               bedrooms + 
               cleaning_fee + 
               availability_30 + 
               neighbourhood + 
               room_type + 
               neighbourhood:cleaning_fee,
           log(price) ~ poly(accommodates, 2) + # 9
               bedrooms + 
               cleaning_fee + 
               availability_30 + 
               neighbourhood + 
               room_type + 
               neighbourhood:cleaning_fee,
           log(price) ~ accommodates + # 10
               poly(bedrooms, 2) + 
               cleaning_fee + 
               availability_30 + 
               neighbourhood + 
               room_type +
               neighbourhood:cleaning_fee,
           log(price) ~ poly(accommodates, 2) + # 11
               poly(bedrooms, 2) + 
               cleaning_fee + 
               availability_30 + 
               neighbourhood + 
               room_type + 
               neighbourhood:cleaning_fee,
           log(price) ~ log(accommodates) + # 12
               bedrooms + 
               cleaning_fee + 
               availability_30 + 
               neighbourhood + 
               room_type + 
               neighbourhood:cleaning_fee,
           log(price) ~ accommodates + # 13
               log(bedrooms + 1) + 
               cleaning_fee + 
               availability_30 + 
               neighbourhood + 
               room_type + 
               neighbourhood:cleaning_fee,
           log(price) ~ log(accommodates) + # 14
               log(bedrooms + 1) + 
               cleaning_fee + 
               availability_30 + 
               neighbourhood + 
               room_type + 
               neighbourhood:cleaning_fee,
           log(price) ~ accommodates + # 15
               bedrooms + 
               cleaning_fee + 
               availability_30 + 
               neighbourhood + 
               room_type + 
               neighbourhood:cleaning_fee +
               availability_30:neighbourhood,
           log(price) ~ poly(accommodates, 2) + # 16
               bedrooms + 
               cleaning_fee + 
               availability_30 + 
               neighbourhood + 
               room_type + 
               neighbourhood:cleaning_fee +
               availability_30:neighbourhood,
           log(price) ~ accommodates + # 17
               poly(bedrooms, 2) + 
               cleaning_fee + 
               availability_30 + 
               neighbourhood + 
               room_type +
               neighbourhood:cleaning_fee +
               availability_30:neighbourhood,
           log(price) ~ poly(accommodates, 2) + # 18
               poly(bedrooms, 2) + 
               cleaning_fee + 
               availability_30 + 
               neighbourhood + 
               room_type +
               neighbourhood:cleaning_fee +
               availability_30:neighbourhood,
           log(price) ~ log(accommodates) + # 19
               bedrooms + 
               cleaning_fee + 
               availability_30 + 
               neighbourhood + 
               room_type + 
               neighbourhood:cleaning_fee +
               availability_30:neighbourhood,
           log(price) ~ accommodates + # 20
               log(bedrooms + 1) + 
               cleaning_fee + 
               availability_30 + 
               neighbourhood + 
               room_type + 
               neighbourhood:cleaning_fee +
               availability_30:neighbourhood,
           log(price) ~ log(accommodates) + # 21
               log(bedrooms + 1) + 
               cleaning_fee + 
               availability_30 + 
               neighbourhood + 
               room_type + 
               neighbourhood:cleaning_fee +
               availability_30:neighbourhood)
```

Function ```ModelSelectionCV``` performs Cross Validation in order to select the model that predicts more accurately in unseen/new/test data, with respect to three different metrics. The following metrics are used: Root Mean Squared Error (RMSE), Mean Absolute Error (MAE), and Median Absolute Error (MedAE). The number of folds and repeats is defined by the user. We have chosen to perform 10-fold CV, repeated 20 times. 

```{r}
ModelSelectionCV = function(data, response, models, numFolds = 10, repeats = 1){
    
    repeatsRMSE = matrix(0, nrow = length(models), ncol = repeats)
    repeatsMedAE = matrix(0, nrow = length(models), ncol = repeats)
    repeatsMAE = matrix(0, nrow = length(models), ncol = repeats)
    
    for (time in 1:repeats){
        
        set.seed(time)
        
        # Randomly shuffle the data
        samp = sample(nrow(data))
        dataShuffled = data[samp, ]
        
        # Create 10 equally size folds
        folds = cut(seq(1, nrow(dataShuffled)), breaks = numFolds, labels = FALSE)
        
        RMSE = matrix(0, nrow = length(models), ncol = numFolds)
        MedAE = matrix(0, nrow = length(models), ncol = numFolds)
        MAE = matrix(0, nrow = length(models), ncol = numFolds)
        
        cat("\n",numFolds, "-Fold CV", " || Repeat ", time, sep = "")
        cat("\n----------------------\n")
        for(model in 1:length(models)){
            
            cat("Model", model,"\n")
            
            for(fold in 1:numFolds){
                
                testIndices = which(folds == fold, arr.ind = TRUE)
                testData = dataShuffled[testIndices, ]
                trainData = dataShuffled[-testIndices, ]
                
                modelTrain = lm(models[[model]], data = trainData, singular.ok = FALSE)
                
                predictions = exp(predict(modelTrain, testData))
                n = nrow(testData) 
                k = length(coef(modelTrain))
                RSS = sum((testData[, response] - predictions)^2)
                
                RMSE[model, fold] = sqrt(RSS/n)
                MedAE[model, fold] = median(abs(testData[, response] - predictions))
                MAE[model, fold] = mean(abs(testData[, response] - predictions))
            }
            
        }
        
        repeatsRMSE[, time] = rowMeans(RMSE)
        repeatsMedAE[, time] = rowMeans(MedAE)
        repeatsMAE[, time] = rowMeans(MAE)
    }
    
    meansRMSE = rowMeans(repeatsRMSE)    
    meansMedAE = rowMeans(repeatsMedAE)    
    meansMAE = rowMeans(repeatsMAE)    
    
    bestModelRMSE = which.min(meansRMSE)
    bestModelMedAE = which.min(meansMedAE)
    bestModelMAE = which.min(meansMAE)
    
    cat("\n\n Model number:", bestModelRMSE,
        "\n RMSE", meansRMSE[bestModelRMSE],
        "\n Model: ", format(models[[bestModelRMSE]]))
    
    cat("\n\n Model number:", bestModelMedAE,
        "\n MedAE", meansMedAE[bestModelMedAE],
        "\n Model:", format(models[[bestModelMedAE]]))
    
    cat("\n\n Model number:", bestModelMAE,
        "\n MAE", meansMAE[bestModelMAE],
        "\n Model:",format(models[[bestModelMAE]]), "\n\n")
}
```

```{r, eval = FALSE}
ModelSelectionCV(airbnb, 'price', models, numFolds = 10, repeats = 20)
```

We select the best model with respect to MAE. The reason for this is that MAE is an easily interpretable metric and more robust to outliers compared to RMSE. The model contains a polynomial term of second order in ```accommodates``` and an interaction between ```neighborhood``` and ```cleaning_fee```. MAE is equal to 31.05 euros.  

## Assumptions of Linear Regression

After choosing the best model with respect to MAE, the assumptions of Linear Regression are examined. Although the assumption of constant variance holds, the residuals are not normally distributed.
```{r}
model = lm(log(price) ~ poly(accommodates, 2) + 
               bedrooms + 
           +    cleaning_fee + 
               availability_30 + 
               neighbourhood + 
               room_type + 
               neighbourhood:cleaning_fee, data = airbnb)
summary(model)$adj.r.squared
qqPlot(model$residuals, 
       ylab = "", 
       xlab = "")
mtext("Residuals", side = 2, line = 2.6, cex = 1)
mtext("Normal Quantiles", side = 1, line = 2.6, cex = 1)

resVarianceDF = data.frame(residuals = model$residuals, fittedValues = model$fitted.values)
ggplot(resVarianceDF, aes(x = model$fitted.values, y = model$residuals)) + 
    geom_point(alpha = 0.4) + 
    labs(x = 'Residuals', y = 'Fitted Values') +
    theme_minimal() +
    theme(text = element_text(size = 13), 
          axis.text.x = element_text(size = 13), 
          axis.text.y = element_text(size = 13))
```

We examine the influence and leverage of observations in the fitted model. For this, we calculate the Cooks Distance. We set as a threshold the value $\frac{4}{n}$, where $n$ the number of observations in the data set. We find 744 observations with Cooks Distance greater than the aforementioned threshold.

```{r}
cooksDistance = cooks.distance(model)
numOutliersCD = sum(cooksDistance > 4 / length(cooksDistance))
```

Due to the large number of influencial observations returned by Cooks Distance, we decided to also examine the studentized residuals. First, we calculate the studentized residuals for each observation in the data set. Those with values greater than the absolute value of three are removed. The new data frame (without the outliers) is called ```airbnb2```. The following plot illustrates the studentized residuals. Those indicated with red have an absolute value greater than or equal to three.

```{r}
studentizedRes = rstudent(model)
studResAbs3 = studentizedRes[abs(studentizedRes) >= 3]
studentizedResDF = data.frame(Residuals = studentizedRes, index = 1:nrow(airbnb))
studentizedResDF$colour = ifelse(abs(studentizedResDF$Residuals) > 3, 'red', 'black')
ggplot(studentizedResDF, aes(index, Residuals)) + 
    geom_point(colour = studentizedResDF$colour, alpha = 0.4) + 
    geom_line(aes(x = index, y = 3),  size = 1, linetype = 'dashed') +
    geom_line(aes(x = index, y = -3),  size = 1, linetype = 'dashed') + 
    labs(y = 'Studentized Residuals', x = 'Index') +
    theme_minimal() +
    theme(text = element_text(size = 13),
          axis.text.x = element_text(size = 13),
          axis.text.y = element_text(size = 13)) + 
    scale_y_continuous(breaks = c(-9, -6, -3, 0, 3, 6, 9))

airbnb2 = airbnb[abs(rstudent(model)) < 3, ]
```

We fit the model again using the ```airbnb2``` data set. The adj. $R^2$ increase, and it is equal to 0.633. As it can be seen from the following plots, the residuals are normally distributed, and the assumption of constant variance holds.

```{r}
model2 = lm(log(price) ~ poly(accommodates, 2) +
                bedrooms + 
                cleaning_fee + 
                availability_30 + 
                neighbourhood + 
                room_type +
                neighbourhood:cleaning_fee, data = airbnb2)
summary(model2)$adj.r.squared
qqPlot(model2$residuals, 
       ylab = "", 
       xlab = "")
mtext("Residuals", side = 2, line = 2.6, cex = 1)
mtext("Normal Quantiles", side = 1, line = 2.6, cex = 1)

resVarianceDF = data.frame(residuals = model2$residuals, fittedValues = model2$fitted.values)
ggplot(resVarianceDF, aes(x = model2$fitted.values, y = model2$residuals)) + 
    geom_point(alpha = 0.4) + 
    labs(x = 'Residuals', y = 'Fitted Values') +
    theme_minimal() +
    theme(text = element_text(size = 13), 
          axis.text.x = element_text(size = 13), 
          axis.text.y = element_text(size = 13))
```

## Model Validation

Function ```ModelValidationCV``` perfroms 10-fold CV in order to examine how well the model predicts the price in unseen/new data. First, observations that correspond to studentized residuals with absolute value greater than three are extracted. In each of the 10 repetitions, the model is fitted in the train set that contains no outliers. A sample of the outliers is added in the test set, so that the latter represents reality, that is, contains both normal and outlier observations. MAE is equal to 31.11 euros, whereas the RMSE and MedAE are 52.64 and 19.88 euros respectively.

```{r}
ModelValidationCV = function(data, response, model, numFolds = 10, seed = 100){
    
    outliers = data[abs(rstudent(model)) >= 3, ]
    dataNoOutliers = data[abs(rstudent(model)) < 3, ]
    numOutliers = nrow(outliers)
    percentOutliers = numOutliers / nrow(data)
    
    set.seed(seed)
    samp = sample(nrow(dataNoOutliers))
    dataShuffled = dataNoOutliers[samp, ]

    # Create 10 equally size folds
    folds = cut(seq(1, nrow(dataNoOutliers)), breaks = numFolds, labels = FALSE)  
    
    RMSE = numeric(numFolds)
    MedAE = numeric(numFolds)
    MAE = numeric(numFolds)
    
    for(fold in 1:numFolds){
        
        testIndices = which(folds == fold, arr.ind = TRUE)
        testData = dataShuffled[testIndices, ]
        trainData = dataShuffled[-testIndices, ]
        sampOutliers = sample(nrow(outliers), round(percentOutliers*nrow(testData)))
        chooseOutliers = outliers[sampOutliers, ]
        testData = rbind(testData, chooseOutliers)
        
        modelTrain = lm(log(price) ~ poly(accommodates, 2) +
                            bedrooms + 
                            cleaning_fee + 
                            availability_30 + 
                            neighbourhood + 
                            room_type +
                            neighbourhood:cleaning_fee,
                        data = trainData, 
                        singular.ok = FALSE)
        
        predictions = exp(predict(modelTrain, testData))
        n = nrow(testData) 
        k = length(coef(modelTrain))
        RSS = sum((testData[, response] - predictions)^2)
    
        RMSE[fold] = sqrt(RSS/n)
        MedAE[fold] = median(abs(testData[, response] - predictions))
        MAE[fold] = mean(abs(testData[, response] - predictions))

    }
    
    meanRMSE = mean(RMSE)
    meanMedAE = mean(MedAE)
    meanMAE = mean(MAE)

    cat("\n\n RMSE", meanRMSE)
    cat("\n\n MedAE:", meanMedAE)
    cat("\n\n MAE:", meanMAE, "\n\n")
    
}
```

```{r}
ModelValidationCV(airbnb, 'price', model)
```